\documentclass[../main.tex]{subfiles}
\usepackage[hmargin=2.5cm,vmargin=3cm,bindingoffset=0.5cm]{geometry}
\graphicspath{{\subfix{../images/}}}

\begin{document}

\textit{This is mostly targeted to certain individuals who carelessly read this guide while cramming.}

\enumerate
    \item \textbf{NOTE THAT THIS GUIDE MAY CONTAIN FACTUAL ERRORS AND MISSING TOPICS!} Although this text aims to be fully comprehensive and aims to cover 100\% of the IGCSE 0478 syllabus, providing extra information for clarity. It may miss some points, or state false information. Therefore, \emph{please do not use this as your sole source of revision.} Report all issues to me (Eason Qin).
    \item The chapter and section markers \textbf{\textit{will not correspond to the textbook directly!}} Some of the content is deemed too trivial to write about; for those sections I urge you to use your textbook.
    \item The subchapter order is also not identical to the textbook. It makes sense for some things to be in one chapter than the other, especially all the networking content.
    \item I expect you to know that this \textbf{is a reference guide}. This is for you to \textbf{refer to.} refer to the table of contents if you need to find something specific. Please also use your own notes and the official to revise.
    \item Please find simpler answers to your questions in the text itself, if I were to help you, I wouldn't be doing much other than paraphrasing the text. If you have fedback, may as well e-mail me.
\endenumerate

\end{document}
